A Pitman-Yor process prior for estimating shared evolutionary events

### 2025-01-17 manuscript/ms.tex
Working on manuscript.
Adding figure of Cyrtodactylus results.

Adding Easley cluster to acknowledgements.

Adding citation for pycoevolity.

When analyzing each simulated \dataset with \ecoevolity,
we ran four MCMC chains for 75,000 generations with a sample taken every 50
generations.
We summarized the last 1000 samples from each chain for a total of 4000 MCMC
samples to approximate the posterior distribution for every simulated \dataset.
From the four chains of each analysis, we calculated the potential
scale reduction factor \citep[PSRF; the square root of Equation 1.1
in][]{Brooks1998} and effective sample size \citep[ESS;][]{Gong2014} for all
continuous parameters and the log likelihood using
\pycoevolity (Commit 27cb15e5).
When plotting results, we highlight any simulation replicates that have a
$\textrm{PSRF} > 1.2$.

@@

\subsection{Empirical application?}

@@

We thank \ldots
This work was supported by funding provided to JRO from the National Science
Foundation (NSF grant number DEB 1656004).
The computational work was made possible by the Auburn University (AU) Hopper
Cluster supported by the AU Office of Information Technology
and
a grant of high-performance computing resources and technical support from the
Alabama Supercomputer Authority.
This paper is contribution number \highLight{XXX} of the Auburn University
Museum of Natural History.

>>>>

When analyzing each simulated \dataset with \ecoevolity,
we ran four MCMC chains for 75,000 generations with a sample taken every 50
generations.
We summarized the last 1000 samples from each chain for a total of 4000 MCMC
samples to approximate the posterior distribution for every simulated \dataset.
From the four chains of each analysis, we calculated the potential
scale reduction factor \citep[PSRF; the square root of Equation 1.1
in][]{Brooks1998} and effective sample size \citep[ESS;][]{Gong2014} for all
continuous parameters and the log likelihood using
\pycoevolity \citep[Commit 27cb15e5;][]{Oaks2018ecoevolity}.
When plotting results, we highlight any simulation replicates that have a
$\textrm{PSRF} > 1.2$.

@@

\subsection{Empirical application}

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/grid-cyrtodactylus-cropped.pdf}
        \captionsetup{listformat=figList}
        \caption{
            Results from the eight pairs of \spp{Cyrtodactylus} populations are
            robust across all three priors on the clustering of divergence
            times.
            We generated the plots using Version 0.2.12 (Commit 06f8bb8) of
            \pycoevolity \citep{Oaks2018ecoevolity} and Version 3.1.3 of
            matplotlib \citep{matplotlib}.
        }
        \label{fig:cyrtresults}
    \end{center}
\end{figure}

@@

We thank \ldots
This work was supported by funding provided to JRO from the National Science
Foundation (NSF grant number DEB 1656004).
The computational work was made possible by the Auburn University (AU) Hopper
and Easley Clusters supported by the AU Office of Information Technology and
a grant of high-performance computing resources and technical support from the
Alabama Supercomputer Authority.
This paper is contribution number \highLight{XXX} of the Auburn University
Museum of Natural History.
